Covariance as constraint: Leveraging leaf economic relationships to constrain plant functional type trait estimates

### 2018-01-08 manuscript-md/02_methods.Rmd
Convert SLA units to kg m-2

Foliar trait data for this analysis comes from the TRY global traits database (@kattge_try_2011; Tab.\ \@ref(tab:trydata)).
We focused our research on seven foliar traits:
Leaf longevity (months),
specific leaf area (SLA, mm$^2$ mg$^{-1}$),
leaf nitrogen content ($N_{mass}$, mg N g$^{-1}$ or $N_{area}$, g m$^{-2}$),
leaf phosphorus content ($P_{mass}$, mg P g$^{-1}$ or $P_{area}$, g m$^{-2}$),
leaf dark respiration at leaf temperature ($R_{d,mass}$, µmol g$^{-1}$ s$^{-1}$, or $R_{d,area}$, µmol m$^{-2}$ s$^{-1}$),
maximum Rubisco carboxylation rate at 25°C ($V_{c,max,mass}$, µmol g$^{-1}$ s$^{-1}$, or $V_{c,max,area}$, µmol m$^{-2}$ s$^{-1}$),
and maximum electron transport rate ($J_{max,mass}$, µmol g$^{-1}$ s$^{-1}$, or $J_{max,area}$, µmol m$^{-2}$ s$^{-1}$).
We performed analyses separately for both mass- and area-normalized traits to avoid potential artifacts caused by different trait normalization [@osnas_global_2013; @lloyd_les].
We restricted our analysis to TRY data that have been quality-controlled and for which adequate species information was provided for functional type classification [see @kattge_try_2011].

>>>>

Foliar trait data for this analysis comes from the TRY global traits database (@kattge_try_2011; Tab.\ \@ref(tab:trydata)).
We focused our research on seven foliar traits:
Leaf longevity (months),
specific leaf area (SLA, m$^2$ kg$^{-1}$),
leaf nitrogen content ($N_{mass}$, mg N g$^{-1}$ or $N_{area}$, g m$^{-2}$),
leaf phosphorus content ($P_{mass}$, mg P g$^{-1}$ or $P_{area}$, g m$^{-2}$),
leaf dark respiration at leaf temperature ($R_{d,mass}$, µmol g$^{-1}$ s$^{-1}$, or $R_{d,area}$, µmol m$^{-2}$ s$^{-1}$),
maximum Rubisco carboxylation rate at 25°C ($V_{c,max,mass}$, µmol g$^{-1}$ s$^{-1}$, or $V_{c,max,area}$, µmol m$^{-2}$ s$^{-1}$),
and maximum electron transport rate ($J_{max,mass}$, µmol g$^{-1}$ s$^{-1}$, or $J_{max,area}$, µmol m$^{-2}$ s$^{-1}$).
We performed analyses separately for both mass- and area-normalized traits to avoid potential artifacts caused by different trait normalization [@osnas_global_2013; @lloyd_les].
We restricted our analysis to TRY data that have been quality-controlled and for which adequate species information was provided for functional type classification [see @kattge_try_2011].
